Accelerated evolution of convective simulations

### 2018-02-28 tex/bvp_paper.tex
updates to conclusion text

\section{Extensions \& Conclusion}
\label{sec:extensions}
In this work we have used \RB convection as a test case for the AE method, but we argue that
the true power of this technique is in its extensions to more complicated studies.
One need only derive the steady-state, horizontally-averaged equations for a given
equation set (e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple that information with knowledge of the boundary conditions
and current dynamics (as described in
section \ref{subsection:ae} and appendix \ref{appendix:recipe}) to achieve a quickly
converged solution. While in-depth studies of AE extensions are beyond the 
scope of this paper, we will briefly describe
areas in which the AE method should be explored.

In conclusion, here we have described a procedure for converging convective simulations using
a method of Accelerated Evolution (AE), and compared it to Standard
Evolution (SE) achieved by running simulations for a thermal timescale.
We have shown that the AE method produces evolved solutions on short timescales
whose dynamics are similar to SE solutions, and we have discussed differences that arise
between the two methods.

We have shown that the AE method is valid at low values of $S$, in which solutions
converge quickly and the thermal timescale is short, but that it is also applicable
at high values of $S$, where SE solutions can take an
intractable amount of time. This shows that the AE method not only progresses
solutions towards the correct evolved state (at high $S$), but that it also does not
remove the simulation from the correct evolved state once such a state is achieved (at low $S$). 
We have studied
the AE method in both 2D and 3D, but have restricted most of our study to 2D flows.
Because the AE technique depends only on horizontally integrated information, 
we examine a select small group
of 3D simulations only to demonstrate the method's efficacy there.

One area in which the AE approach can be applied is to simple studies of
internally heated convection \cite{goluskin2016}.  The least complex of these studies 
examine the incompressible Boussinesq equations, as presented in this work,
but include a constant source term in the energy equation. The evolved convective
state in such internally heated systems includes a flux profile whose value linearly
increases with height, as the volumetric heating requires the convection to carry
more flux towards the top of the domain.  These systems can be straightforwardly
studied using the methods that we examined here, while scaling the profiles derived
in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux.

Studies of stratified convection are likely to gain the most through
developing and employing the AE method.
In many studies of stratified convection, the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}. Thus, the
thermal timescale is much larger deep in the atmosphere, where density is high and diffusivity
is very low, than it is near the surface.  As such, runs at similar supercriticalities
but with different degrees of stratification can have thermal timescales which
differ by orders of magnitude.  Fortunately, the AE method is easily adapted to
the simplest stratified, compressible systems.  Rather than studying the total
flux through the domain, it is essential to study only the flux in excess of 
what is conducted along the adiabatic temperature gradient while constructing
the profiles in Eqn. (\ref{eqn:bvp_ratios}).  
Furthermore, in addition to solving for
hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously
ensure that mass is conserved.  Thus, additional equations and boundary conditions
must be used to ensure that mass is not created or destroyed,
in a manner similar to how mass is treated in stellar structure codes
\cite{paxton&all2011}.

Studies of convection frequently examine paired stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
When the interface between the stable region
and the convecting region is stiff and motions do not cross that interface,
convective motions cannot accelerate the restratification of the stable region.
In fully-convective domains, such as those studied in this work, the thermodynamics evolve
at a more rapid rate than the thermal diffusion time across the domain due to
the help of convective motions.  For example, in Fig. \ref{fig:time_trace}a,
the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
despite the thermal timescale being roughly $10^4$ freefall units.

Stellar structure + 3-2-1 D \cite{arnett&all2015, cristini&all2016}. The
latter paper focuses on mixing on the boundaries of convective regions.

>>>>

\section{Extensions \& Conclusion}
\label{sec:extensions}
In this work, we have studied a method of Accelerated Evolution (AE) which can
be employed to achieve rapid thermal convergence of convective simulations.  We compared
this technique to the Standard Evolution (SE) of convection through a thermal diffusion timescale and
showed that AE rapidly obtains solutions whose dynamics are similar to SE solutions.
The AE method is not only valid at low values of $S$, where SE solutions
converge quickly due to the short thermal timescale, but AE is also applicable
at high values of $S$, where SE solutions are intractable.
We have studied
the AE method in both 2D and 3D, but restricted most of our study to 2D flows;
AE depends only on the 1D horizontal average of quantities, and our inclusion of 3D
simulations was merely to demonstrate the broadly useful nature of AE.

Here we studied \RB convection as a test case for the AE method, but we argue that
the true power of this technique is in its extensions to more complicated studies.
To achieve AE in more complicated systems, one need only derive 
the steady-state, horizontally-averaged equations governing
the convective dynamics
(e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple those equations with knowledge of the boundary conditions
and current dynamics as described in
section \ref{subsection:ae} and appendix \ref{appendix:recipe}.
While in-depth studies of AE extensions are beyond the 
scope of this paper, we will briefly discuss
avenues in which the AE method should be explored and tested.

Convection in natural systems is often driven by internal heating processes
rather than imposed, fixed boundary condditions. The AE procedure can be straightforwardly
applied to Boussinesq studies of internally heated convection \cite{goluskin2016},
where a constant source term in the energy equation causes 
the vertical flux through the system to increase with height.
These systems can be straightforwardly
studied using exactly the methods that we examined here, but 
scaling the flux profiles derived
in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux. Studies of
convection in natural system often employ height-dependent conductivities
\cite{brandenburg2016}, leading
to natural flux divergences that act as internal heating terms, and the study
of this method in the simple internal heating context will be an important step
towards achieving AE in simulations with astrophysically realistic conductivities.

In order to understand the influences of overshooting convection, some
studies examine adjacent stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
When the interface between the stable region
and the convecting region is stiff and motions do not cross that interface,
convective motions cannot accelerate the restratification of the stable region.
In fully-convective domains, such as those studied in this work, the thermodynamics evolve
at a more rapid rate than the thermal diffusion time across the domain due to
the help of convective motions.  For example, in Fig. \ref{fig:time_trace}a,
the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
despite the thermal timescale being roughly $10^4$ freefall units. However, in 
studies where there is a stable region which is not mixed by convection, the experimentalist
must either wait through a thermal diffusion time for the region to restratify
or employ methods such as the AE method to study evolved atmospheres.

Studies of stratified, compressible convection have much to gain through
developing and employing AE.
In many studies of stratified convection, the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}. Thus, the
thermal timescale grows with depth in the atmosphere, and
the difficulty of achieving thermal convergence grows as simulators study more highly
stratified domains.
In order to extend AE into this regime, two additional pieces of information must be considered.
First, rather than constructing the profiles in Eqn. (\ref{eqn:bvp_ratios})
with the total flux through the domain, only the superadiabatic portion of
the flux should be considered.
Second, in addition to solving for
hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously evolve the density
profile in a manner which conserves mass.  In a 1D boundary value problem, such as
is solved to achieve AE here, this implies the inclusion of an equation which tracks
the vertically integrated mass, and sets boundary conditions on that mass to ensure
that no mass enters or leaves the domain.

A long-term goal would be to extend AE in a robust way such that it can be
incorporated into stellar structure codes. Current state of the art stellar structure
models are 1D solves that parameterize convection through widely accepted models
like Mixing Length Theory \cite{paxton&all2011}. Recently, researches have begun
efforts to couple evolution of stellar structure on significant thermal timescales
while resolving convective dynamics.  A first attempt to do this was through the
use of fully nonlinear implicit timestepping methods 
\cite{viallet&all2011, viallet&all2013, viallet&all2016},
but the emergence of unrealistic dynamics when timesteps are so large that they
don't properly resolve advective motions has made this an unlikely means of
evolving systems for long times. Other recent work, 
such as 3-2-1D \cite{arnett&all2015} convection, which uses information in
evolved 3D dynamical solutions to evolve the 1D underlying thermodynamic profile,
and which is similar to the method we presented here, shows promise.  Some other
work pairing 1D solves with fully nonlinear 3D solutions has been conducted
\cite{cristini&all2016}, but often in more complicated systems than those we examine here. 
Through small improvements and extensions, the AE method here can be improved
and verified until it is capable of handling the full physics present in nonlinear
stellar evolution.
